A practical look at genetic algorithms

### 2015-11-21 evolutionaryComputation/practicals/report.tex
this build runs but it doesn't find no solutions...
tried doing a stocastic one in this way, but realized its wrong
implmeneted the stoastic thingy

About randomly linked:
	There is another way to do it: for every member randomly link
	differently, and randomly pick 1 randomly linked instructionset
	for offspring generation (or do the strongest).
	Currently I do the global randomly linked, every run will however
	have the same randomly linked value, I'm aware of this.
\section{Execution}
%TODO:
% 1. Experiments
%	Create tables % including:
%		* min pop size for 29 out of 30 runs successful.
%		* The average number of generations
%		* The average CPU time required for running the GA with minimal pop size
%		* average should be over 30 runs
%	Draw a graph from the experiments
%		* pop size on x, # succes on Y
% maybe some more testing of the crossovers?
% also try to implement a threading scheme??

>>>>

About randomly linked:
	There is another way to do it: for every member randomly link
	differently, and randomly pick 1 randomly linked instructionset
	for offspring generation (or do the strongest).
	Currently I do the global randomly linked, every run will however
	have the same randomly linked value, I'm aware of this.

I'm not quite sure about the graphs. I have to show the number of successes
out of the 30 runs, but this is already set in stone, because its either
29 or 30, or its no successes.

The stocastic ensursance wants to make sure that 29 out of 30 runs are
'good enough', but combining this with the bidisectional search is difficult.
because the bidisectional search may happen to end up just higher than possible.

I considered to combine the bidisectional search with the stocastic ensurance.
But that would be way slower, and it won't be much better (or even worse depending
on how you do it) then my current implementation.

\section{Execution}
%TODO:
% 1. Experiments
% Make the actuall expiriment work\dots
%	Create tables % including:
%		* min pop size for 29 out of 30 runs successful.
%		* The average number of generations
%		* The average CPU time required for running the GA with minimal pop size
%		* average should be over 30 runs
%	Draw a graph from the experiments
%		* pop size on x, # succes on Y
% maybe some more testing of the crossovers?
% also try to implement a threading scheme??
